\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-20 icse/compiler.tex
Small changed for Section 4

\subsection{Token List Parser}
Parsing rules determine the token list parser, and each parsing rule
is written in extended Scala parser combinators.  We modified the
meaning of the alternative composition operator ( \( | \) ) to collect
all the longest matched results.  If a parser detects a step that
cannot be parsed with given parsing rules, it reports the step into
{\sf Rule Assistant}.  Even when a parser parses a step successfully,
it also reports the step if it can parse the step in multiple ways.
We use Packrat parsing~\cite{packrat} for parsing rules, which
support left recursion.

@@

Consider the following example parsing rule, which is a simplified
version for the step 2-e-i of the \textbf{ToPrimitive} algorithm.
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
val Expr = (          // expressions
  varT ^^ ... |       // identifiers
  "?" ~ Expr ^^ ... | // return if abrupt
                      // function calls
  word ~ "(" ~ repsep(Expr, ",") ~ ")" ^^ ... |
  "<<" ~ repsep(varT, ",") ~ ">>" ^^ ...  // lists
)
\end{lstlisting}
The \( \code{Stmt} \) compile rule describes how to compile statements
with one parsing rule and its conversion rule is omitted for now for
brevity.  The \( \code{Expr} \) compile rule describes how to compile
expressions with four parsing rules.  A token parser with the above
rules parses the step 2-e-i of \textbf{ToPrimitive} to the following
token AST:
\begin{center}
\includegraphics[width=0.5\textwidth]{img/token_ast.png}
\end{center}

\subsection{Token AST Converter}
Conversion rules describe how to generate an \( \ires \) function for a
given token AST.  Each conversion rule is defined with its
corresponding parsing rule.  For basic token parsers, their conversion
rules always return the string values of the contents in parsed tokens.
For example, the following conversion rules are the omitted parts
in the previous example for the step 2-e-i of \textbf{ToPrimitive}:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
val Expr = (               // expressions
  ... ^^ { x => EId(x) } | // identifiers
                           // return if abrupt
  ... ^^ { _ ~ e => EReturnIfAbrupt(e) } |
                           // function calls
  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) } |
  ... ^^ { case _ ~ x ~ _ => EList(e) } // lists
)
\end{lstlisting}
The conversion rule of the compile rule \( \code{Stmt} \) uses only
the second and fourth sub trees and converts them to \( \ires \)
components.  The second sub-tree is converted to a string value
because it was constructed via the basic token parser \( \code{varT} \).
The fourth sub-tree is converted to an \( \ires \) expression
because the conversion rules of the \( \code{Expr} \) compile rule
construct \( \ires \) expressions.  Then, the conversion rule of
\( \code{Stmt} \) constructs the lexical binding instruction \( \code{ILet} \)
with the string value and the \( \ires \) expression.  In this way,
the step 2-e-i of \textbf{ToPrimitive} is converted to the following
instruction:
\begin{lstlisting}[style=ires]
let result = ? (Call exoticToPrim input (new [hint]))
\end{lstlisting}

@@

\item \textbf{Abstract data types:} \( \ires \) supports only three
abstract data types: \( \code{Record} \) for mappings from some values
to other values, \( \code{List} \) for sequential data, and
\( \code{Singleton} \) for singleton data.  For example, ECMAScript
environment records are represented as \( \code{Record} \)
with string values as keys and addresses as values.  Each key
represents an identifier name and its corresponding address represents
an ECMAScript object.  We also represent constants in the ECMAScript
specification such as \( \code{empty} \) and \( \code{normal} \) as
\( \code{Singleton} \) data types in \( \ires \).
\end{itemize}

@@

The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
For a given failed step $T$ and the size of a failed input $n$, it
attempts to find a set of the most specific suggestions.  It
substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
special token \( \tstar \), which represents some sub-sequence of a
failed step.  It collects a set of possible suggestions, and then
removes more general ones than existing suggestions.  To support this
process, we added a parsing rule  \( \code{starT} \) to each compile
rule as follows:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... | starT ^^ { case x => Dummy("Stmt") }
// expressions
val Expr = ... | starT ^^ { case x => Dummy("Expr") }
\end{lstlisting}
where \( \code{starT} \) is a special basic token parser that just
checks whether a given token is the special token \( \tstar \). 
Its corresponding conversion rule is a function that returns a dummy
\( \ires \) component \( \code{Dummy} \) with a string value that
represents the name of its compile rule.

>>>>

\subsection{Token List Parser}
Parsing rules determine the token list parser, and each parsing rule
is written in extended Scala parser combinators.  We modified the
meaning of the alternative composition operator ( \( ||| \) ) to collect
all the longest matched results.  If a parser detects a step that
cannot be parsed with given parsing rules, it reports the step into
{\sf Rule Assistant}.  Even when a parser parses a step successfully,
it also reports the step if it can parse the step in multiple ways.
We use Packrat parsing~\cite{packrat} for parsing rules, which
support left recursion.

@@

Consider the following example parsing rule, which is a simplified
version for the step 2-e-i of the \textbf{ToPrimitive} algorithm.
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
// expressions
val Expr =
  // identifiers        // return if abrupt
  varT      ^^ ... |||  "?" ~ Expr      ^^ ... |||
  // function calls
  word ~ "(" ~ repsep(Expr, ",") ~ ")"  ^^ ... |||
  // lists
  "<<" ~ repsep(varT, ",") ~ ">>"       ^^ ...
\end{lstlisting}
The \( \code{Stmt} \) compile rule describes how to compile statements
with one parsing rule and its conversion rule is omitted for now for
brevity.  The \( \code{Expr} \) compile rule describes how to compile
expressions with four parsing rules.  A token parser with the above
rules parses the step 2-e-i of \textbf{ToPrimitive} to the following
token AST:
\begin{center}
\includegraphics[width=0.5\textwidth]{img/token_ast.png}
\end{center}

\subsection{Token AST Converter}
Conversion rules describe how to generate an \( \ires \) function for a
given token AST.  Each conversion rule is defined with its
corresponding parsing rule.  For basic token parsers, their conversion
rules always return the string values of the contents in parsed tokens.
For example, the following conversion rules are the omitted parts
in the previous example for the step 2-e-i of \textbf{ToPrimitive}:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
// expressions
val Expr =
  // identifiers   // return if abrupt
  ... ^^ EId |||   ... ^^ { _ ~ e => EAbrupt(e) } |||
  // function calls
  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) }    |||
  // lists
  ... ^^ { case _ ~ x ~ _ => EList(e) }
)
\end{lstlisting}
The conversion rule of the compile rule \( \code{Stmt} \) uses only
the second and fourth sub trees and converts them to \( \ires \)
components.  The second sub-tree is converted to a string value
because it was constructed via the basic token parser \( \code{varT} \).
The fourth sub-tree is converted to an \( \ires \) expression
because the conversion rules of the \( \code{Expr} \) compile rule
construct \( \ires \) expressions.  Then, the conversion rule of
\( \code{Stmt} \) constructs the lexical binding instruction \( \code{ILet} \)
with the string value and the \( \ires \) expression.  In this way,
the step 2-e-i of \textbf{ToPrimitive} is converted to the following
instruction:
\begin{lstlisting}[style=ires]
let result = ? (Call exoticToPrim input (new [hint]))
\end{lstlisting}

@@

\item \textbf{Abstract data types:} \( \ires \) supports only three
abstract data types: \( \code{Record} \) for mappings from some values
to other values, \( \code{List} \) for sequential data, and
\( \code{Singleton} \) for singleton data.  For example, ECMAScript
environment records are represented as \( \code{Record} \)
from string values into addresses that represents other type of
\( \code{Record} \) for bindings.  We also represent constants
in the ECMAScript specification such as \( \code{empty} \)
and \( \code{normal} \) as \( \code{Singleton} \) data types
in \( \ires \).
\end{itemize}

@@

The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
For a given failed step $T$ and the size of a failed input $n$, it
attempts to find a set of the most specific suggestions.  It
substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
special token \( \tstar \), which represents some sub-sequence of a
failed step.  It collects a set of possible suggestions, and then
removes more general ones than existing suggestions.  To support this
process, we added a parsing rule  \( \code{starT} \) to each compile
rule as follows:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
// expressions
val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
\end{lstlisting}
where \( \code{starT} \) is a special basic token parser that just
checks whether a given token is the special token \( \tstar \). 
Its corresponding conversion rule is a function that returns a dummy
\( \ires \) component \( \code{Dummy} \) with a string value that
represents the name of its compile rule.
